Towards a standardized evaluation of imputation methodology

### 2022-09-20 Manuscript/Towards_a_standardized_evaluation_of_imputation_methodology.tex
final text/bib/img update

\documentclass[bimj,fleqn]{w-art}
\usepackage{times}
\usepackage{w-thm}
\usepackage[authoryear]{natbib}
\usepackage{amsfonts}
\usepackage{graphicx, latexsym}
% \setlength{\bibsep}{2pt}
% \setlength{\bibhang}{2em}
% \newcommand{\J}{J\"{o}reskog}
% \newcommand{\So}{S\"{o}rbom}
% \newcommand{\bcx}{{\bf X}}
% \newcommand{\bcy}{{\bf Y}}
% \newcommand{\bcz}{{\bf Z}}
% \newcommand{\bcu}{{\bf U}}
% \newcommand{\bcv}{{\bf V}}
% \newcommand{\bcw}{{\bf W}}
% \newcommand{\bci}{{\bf I}}
% \newcommand{\bch}{{\bf H}}
% \newcommand{\bcb}{{\bf B}}
% \newcommand{\bcr}{{\bf R}}
% \newcommand{\bcm}{{\bf M}}
% \newcommand{\bcf}{{\bf F}}
% \newcommand{\bcg}{{\bf G}}
% \newcommand{\bcs}{{\bf S}}
% \newcommand{\bca}{{\bf A}}
% \newcommand{\bcd}{{\bf D}}
% \newcommand{\bcc}{{\bf C}}
% \newcommand{\bce}{{\bf E}}
% \newcommand{\ba}{{\bf a}}
% \newcommand{\bb}{{\bf b}}
% \newcommand{\bc}{{\bf c}}
% \newcommand{\bd}{{\bf d}}
% \newcommand{\bx}{{\bf x}}
% \newcommand{\by}{{\bf y}}
% \newcommand{\bz}{{\bf z}}
% \newcommand{\bu}{{\bf u}}
% \newcommand{\bv}{{\bf v}}
% \newcommand{\bh}{{\bf h}}
% \newcommand{\bl}{{\bf l}}
% \newcommand{\be}{{\bf e}}
% \newcommand{\br}{{\bf r}}
% \newcommand{\bw}{{\bf w}}
% \newcommand{\de}{\stackrel{D}{=}}
% \newcommand{\bt}{\bigtriangleup}
% \newcommand{\bfequiv}{\mbox{\boldmath $\equiv$}}
% \newcommand{\bmu}{\mbox{\boldmath $\mu$}}
% \newcommand{\bnu}{\mbox{\boldmath $\nu$}}
% \newcommand{\bxi}{\mbox{\boldmath $\xi$}}
% \newcommand{\btau}{\mbox{\boldmath $\tau$}}
% \newcommand{\bgamma}{\mbox{\boldmath $\Gamma$}}
% \newcommand{\bphi}{\mbox{\boldmath $\Phi$}}
% \newcommand{\bfphi}{\mbox{\boldmath $\varphi$}}
% \newcommand{\bfeta}{\mbox{\boldmath $\eta$}}
% \newcommand{\bpi}{\mbox{\boldmath $\Pi$}}
% \newcommand{\bequiv}{\mbox{\boldmath $\equiv$}}
% \newcommand{\bvarepsilon}{\mbox{\boldmath $\varepsilon$}}
% \newcommand{\btriangle}{\mbox{\boldmath $\triangle$}}
% \newcommand{\bdelta}{\mbox{\boldmath $\Delta$}}
% \newcommand{\beps}{\mbox{\boldmath $\epsilon$}}
% \newcommand{\btheta}{\mbox{\boldmath $\theta$}}
% \newcommand{\balpha}{\mbox{\boldmath $\alpha$}}
% \newcommand{\bsphi}{\mbox{\boldmath $\varphi$}}
% \newcommand{\bsig}{\mbox{\boldmath $\sigma$}}
% \newcommand{\bfpsi}{\mbox{\boldmath $\psi$}}
% \newcommand{\bfdelta}{\mbox{\boldmath $\delta$}}
% \newcommand{\bsigma}{{\bf \Sigma}}
% \newcommand{\bzero}{{\bf 0}}
% \newcommand{\bpsi}{\mbox{\boldmath $\Psi$}}
% \newcommand{\bep}{\mbox{\boldmath $\epsilon$}}
% \newcommand{\bomega}{\mbox{\boldmath $\Omega$}}
% \newcommand{\bfomega}{\mbox{\boldmath $\omega$}}
% \newcommand{\blambda}{\mbox{\boldmath $\Lambda$}}
% \newcommand{\bflambda}{\mbox{\boldmath $\lambda$}}
% \newcommand{\bfsigma}{\mbox{\boldmath $\sigma$}}
% \newcommand{\bfpi}{{\mbox{\boldmath $\pi$}}}
% \newcommand{\bupsilon}{\mbox{\boldmath $\upsilon$}}
% \newcommand{\obs}{{\rm obs}}
% \newcommand{\mis}{{\rm mis}}
% \theoremstyle{plain}
% \newtheorem{criterion}{Criterion}
% \theoremstyle{definition}
% \newtheorem{condition}[theorem]{Condition}
% \usepackage[]{graphicx}
% \chardef\bslash=`\\ % p. 424, TeXbook
% \newcommand{\ntt}{\normalfont\ttfamily}
% \newcommand{\cn}[1]{{\protect\ntt\bslash#1}}
% \newcommand{\pkg}[1]{{\protect\ntt#1}}
% \let\fn\pkg
% \let\env\pkg
% \let\opt\pkg
% \hfuzz1pc % Don't bother to report overfull boxes if overage is < 1pc
% \newcommand{\envert}[1]{\left\lvert#1\right\rvert}
% \let\abs=\envert

@@

\begin{abstract}
Developing new imputation methodology has become a very active field. Unfortunately, there is no consensus on how to perform simulation studies to evaluate the properties of imputation methods. In this paper, we propose a move towards a standardized evaluation of imputation methodology. To demonstrate the need for standardization, we highlight a set of potential pitfalls that bring forth a chain of potential problems in the objective assessment of the performance of imputation routines. This may lead to sub-optimal use of  imputation in practice. Additionally, we suggest a course of action for simulating and evaluating missing data problems. [TODO: Narrowing the scope of the manuscript to the evaluation of methodology for statistical inference, not prediction or causal inference (although inferential validity encompasses predictive validity and may thus be generalized?). Emphasizing that the ideal evaluation of imputation methodology depends on the aim of the specific study (i.e. how the evaluated methods are used in practice). Split up the problems with the simulation setup/evaluation and the problems with the interpretation/extrapolation from these simulation studies. See e.g. \citet{gree17} on cognitive problem of generelization versus methodological problems. Explain how the standardisation leads to more neutrality, but that this is just a set of elements to consider/report, not a complete 'cookbook'. Add that we focus on  simulation studies evaluating imputation methodology for statistical inference.]
\end{abstract}

@@

When evaluating the statistical properties - and thereby the practical applicability - of imputation methodology, researchers most often make use of simulation studies. Such studies are typically composed of an analysis pipeline in which data are subsequently generated, made incomplete, and imputed repeatedly under different simulation conditions. A set of evaluation criteria is then postulated to evaluate the performance of one or more missing data methods. Recent attention on best practices for method evaluation by means of simulation \citep{morr18}. and **REF MISSING** \citet{pawe22}'s advice to pre-register simulation protocols will guide methodologist in conceptualizing their simulation workflow. However, there is no consensus on how to design, execute and report simulation studies aimed to evaluate imputation methodology. Without a `gold standard' for evaluation, the validity and comparability of simulation setups may differ tremendously from one developer to another. This brings forth a chain of potential problems in the objective assessment of imputation method performance within and across studies, which could lead to sub-optimal use of imputation in practice.

@@

Before setting up a simulation study, the simulator should clearly define and describe the scope of their evaluations. If the simulation parameters are unclear, any methodological problems with simulation study design may be obfuscated by the cognitive problem of generalization \citep{gree17}. For example, misinterpretation and (unintended) questionable research practices can prompt extrapolation beyond the scope of the simulations \citep{gree17, pawe22}. Imputation methods that seem to work well in simulations may then not be suitable in practice, when applied on incomplete empirical data.

One potential reason for discrepancies between imputation method performance in simulations versus applications is the use of sampling variance in the simulation design. Simulation studies on missing data methodology have the unique option to exclude sampling variance from their evaluations and only use the missing data generation procedure as the source of Monte Carlo variation \citep{vink14}. If sampling variance is not of interest, a single complete data set can serve as comparative truth in all simulation repetitions (as opposed to a `standard' simulation setup, in which data is drawn every repetition). After all, we are interested in solving for the missingness and have no need for the noise induced by the sampling mechanism for evaluation in such studies.

@@

A well-designed simulation does not guarantee fair evaluations. Estimands and other simulation targets should be clearly and unambiguously defined in the context of the study aim \citet{pete14}. The number of simulation repetitions may be informed by the required level of precision in the simulation study \citep[e.g. as determined from a maximum tolerable level of uncertainty in terms of a performance measure's Monte Carlo error; see][]{morr18}. The simulation design should ideally be fully factorial, i.e. varying each simulation condition against all other conditions. There may, for example, be interactions between the source and amount of missingness in the incomplete data and the efficacy of imputation methods (i.e., the validity of the assumed missingness mechanism becomes increasingly important with higher missingness proportions) \citep{scho18}. If there is more than one imputation method under evaluation, the simulation design should apply each method to every incomplete data set. Applying all methods to the same incomplete data set is computationally convenient, and minimizes unnecessary variation, which makes for fairer comparisons.

@@

% [TODO: split up into data and missingness part of the DGM, with choices between data sources, missingness mechanisms and proportions. And divide problems between simulation and interpretation, see Reviewer 2: "whether method A (e.g. imputation) outperforms method B (e.g. listwise deletion) depends on the estimand, purpose of the study, used distributions (in the DGP, imputation model, possibly also analysis model), and simulation setup (e.g. dependency structure) - if a human misinterprets findings in a comparison of method A and B, then this is a cognitive problem and not the problem on how missingness was generated in the DGP."]

[TODO; describe problems with data generation and interpretation: If the source of the data is model-based, the correlations in the data may be so high that there is no effective missingness due to the predictive power in the other variables, and the data source may be unfair if the data generating model is equal to one of the imputation models under evaluation. With a design-based simulation, the data source is unlikely to have no missingness and the choice of initial missing data method may propagate into the evaluations.]

@@

\begin{figure}[ht!]
  \resizebox{\textwidth}{!}{ %notice the \resizebox{} command
        \includegraphics{plots/plot_mmech.pdf}
  }      
  \caption{Three different realizations of missingness generation for MCAR and right-tailed MAR missingness mechanisms for different levels of correlation $\rho$ between the variable to ampute and the covariates that guide the probability to be missing. Note that the conditional probabilities of MCAR and right-tailed MAR ($\rho=0$) are identical.}
    \label{Fig4}
\end{figure}

@@

The evaluation of simulated results goes far beyond plausibility and distributional characteristics. The quality and validity of an imputation task will also rely on the relation between the missing data models, imputation models, and analysis models. When an imputation model is able to capture the essence of the true non-response mechanism relative to the analysis model, the models are said to be congenial \citep{meng94}. [TODO: change this to being able to embed the analysis procedure and the imputation model within a Bayesian model; the nonresponse model may be misspecified while the imputation procedure is congenial.] The congeniality of all imputation models should be assessed, but methods to assess the suitability of imputation models and diagnose misfit often rely on visual inspection of the imputations \citep[see e.g.][]{abayomi2008diagnostics, bond16}. This makes its assessment a challenging and timeconsuming endeavor in many simulation studies.

@@

@@

\begin{table}[ht]
\caption{Checklist for reporting on imputation methodology evaluations.}
\label{table:check}
\begin{tabular}{ll}
% \hline
%   & Suggested aspects to report                                                       \\
\hline
1 & Simulation scope                                                                   \\ \cline{2-2}
$\square$  & Aim                                                                                \\
$\square$  & Design (incl. pseudo-code or flow diagram)                                         \\
$\square$  & Number of simulation repetitions                                                   \\ \hline
2 & Comparative truth                                                                  \\ \cline{2-2}
$\square$  & Data source (model-based or design-based)                                           \\
$\square$  & Sampling variance                                                                  \\
%  & Data characteristics (number of observations, number of variables, variable types, \\
%  & coherence between variables incl. data structures e.g. clustering)                 \\
$\square$  & Data characteristics (incl. multivariate relations and structures e.g. clustering) \\
$\square$  & Estimand                                                                           \\ \hline 
3 & Induced missingness                                                                \\ \cline{2-2}
$\square$  & Missingness mechanism (incl. type or functional form of the missing data   model)  \\
$\square$  & Missingness pattern (incl. missingness proportion)                                 \\ \hline 
4 & Applied methods                                                                    \\ \cline{2-2}
$\square$  & Imputation methods (incl. parameters e.g. the number of imputations)               \\
$\square$  & Analytic methods (incl. calculation of standard errors e.g. pooling   rules)       \\
$\square$  & Reference method (e.g. complete case analysis)                                    \\ \hline 
5 & Imputation evaluation                                                              \\ \cline{2-2}
$\square$  & Imputation-generating process (e.g. algorithmic non-convergence)                   \\
$\square$  & Imputation model fit (e.g. posterior predictive checks)                            \\
$\square$  & Distributional characteristics (e.g. plausibility of imputed values)               \\ \hline 
6 & Performance evaluation                                                             \\ \cline{2-2}
$\square$  & Statistical properties (e.g. confidence validity)                                  \\
$\square$  & Comparative performance (e.g. predictive accuracy)                                 \\ \hline
\end{tabular}
\end{table}

>>>>

\documentclass[bimj,fleqn]{w-art}
\usepackage{times}
\usepackage{w-thm}
\usepackage[authoryear]{natbib}
\usepackage{amsfonts}
\usepackage{epstopdf}
\usepackage{graphicx, latexsym}
% \setlength{\bibsep}{2pt}
% \setlength{\bibhang}{2em}
% \newcommand{\J}{J\"{o}reskog}
% \newcommand{\So}{S\"{o}rbom}
% \newcommand{\bcx}{{\bf X}}
% \newcommand{\bcy}{{\bf Y}}
% \newcommand{\bcz}{{\bf Z}}
% \newcommand{\bcu}{{\bf U}}
% \newcommand{\bcv}{{\bf V}}
% \newcommand{\bcw}{{\bf W}}
% \newcommand{\bci}{{\bf I}}
% \newcommand{\bch}{{\bf H}}
% \newcommand{\bcb}{{\bf B}}
% \newcommand{\bcr}{{\bf R}}
% \newcommand{\bcm}{{\bf M}}
% \newcommand{\bcf}{{\bf F}}
% \newcommand{\bcg}{{\bf G}}
% \newcommand{\bcs}{{\bf S}}
% \newcommand{\bca}{{\bf A}}
% \newcommand{\bcd}{{\bf D}}
% \newcommand{\bcc}{{\bf C}}
% \newcommand{\bce}{{\bf E}}
% \newcommand{\ba}{{\bf a}}
% \newcommand{\bb}{{\bf b}}
% \newcommand{\bc}{{\bf c}}
% \newcommand{\bd}{{\bf d}}
% \newcommand{\bx}{{\bf x}}
% \newcommand{\by}{{\bf y}}
% \newcommand{\bz}{{\bf z}}
% \newcommand{\bu}{{\bf u}}
% \newcommand{\bv}{{\bf v}}
% \newcommand{\bh}{{\bf h}}
% \newcommand{\bl}{{\bf l}}
% \newcommand{\be}{{\bf e}}
% \newcommand{\br}{{\bf r}}
% \newcommand{\bw}{{\bf w}}
% \newcommand{\de}{\stackrel{D}{=}}
% \newcommand{\bt}{\bigtriangleup}
% \newcommand{\bfequiv}{\mbox{\boldmath $\equiv$}}
% \newcommand{\bmu}{\mbox{\boldmath $\mu$}}
% \newcommand{\bnu}{\mbox{\boldmath $\nu$}}
% \newcommand{\bxi}{\mbox{\boldmath $\xi$}}
% \newcommand{\btau}{\mbox{\boldmath $\tau$}}
% \newcommand{\bgamma}{\mbox{\boldmath $\Gamma$}}
% \newcommand{\bphi}{\mbox{\boldmath $\Phi$}}
% \newcommand{\bfphi}{\mbox{\boldmath $\varphi$}}
% \newcommand{\bfeta}{\mbox{\boldmath $\eta$}}
% \newcommand{\bpi}{\mbox{\boldmath $\Pi$}}
% \newcommand{\bequiv}{\mbox{\boldmath $\equiv$}}
% \newcommand{\bvarepsilon}{\mbox{\boldmath $\varepsilon$}}
% \newcommand{\btriangle}{\mbox{\boldmath $\triangle$}}
% \newcommand{\bdelta}{\mbox{\boldmath $\Delta$}}
% \newcommand{\beps}{\mbox{\boldmath $\epsilon$}}
% \newcommand{\btheta}{\mbox{\boldmath $\theta$}}
% \newcommand{\balpha}{\mbox{\boldmath $\alpha$}}
% \newcommand{\bsphi}{\mbox{\boldmath $\varphi$}}
% \newcommand{\bsig}{\mbox{\boldmath $\sigma$}}
% \newcommand{\bfpsi}{\mbox{\boldmath $\psi$}}
% \newcommand{\bfdelta}{\mbox{\boldmath $\delta$}}
% \newcommand{\bsigma}{{\bf \Sigma}}
% \newcommand{\bzero}{{\bf 0}}
% \newcommand{\bpsi}{\mbox{\boldmath $\Psi$}}
% \newcommand{\bep}{\mbox{\boldmath $\epsilon$}}
% \newcommand{\bomega}{\mbox{\boldmath $\Omega$}}
% \newcommand{\bfomega}{\mbox{\boldmath $\omega$}}
% \newcommand{\blambda}{\mbox{\boldmath $\Lambda$}}
% \newcommand{\bflambda}{\mbox{\boldmath $\lambda$}}
% \newcommand{\bfsigma}{\mbox{\boldmath $\sigma$}}
% \newcommand{\bfpi}{{\mbox{\boldmath $\pi$}}}
% \newcommand{\bupsilon}{\mbox{\boldmath $\upsilon$}}
% \newcommand{\obs}{{\rm obs}}
% \newcommand{\mis}{{\rm mis}}
% \theoremstyle{plain}
% \newtheorem{criterion}{Criterion}
% \theoremstyle{definition}
% \newtheorem{condition}[theorem]{Condition}
% \usepackage[]{graphicx}
% \chardef\bslash=`\\ % p. 424, TeXbook
% \newcommand{\ntt}{\normalfont\ttfamily}
% \newcommand{\cn}[1]{{\protect\ntt\bslash#1}}
% \newcommand{\pkg}[1]{{\protect\ntt#1}}
% \let\fn\pkg
% \let\env\pkg
% \let\opt\pkg
% \hfuzz1pc % Don't bother to report overfull boxes if overage is < 1pc
% \newcommand{\envert}[1]{\left\lvert#1\right\rvert}
% \let\abs=\envert

@@

\begin{abstract}
Developing new imputation methodology has become a very active field. Unfortunately, there is no consensus on how to perform simulation studies to evaluate the properties of imputation methods. In part this may be due to different aims between fields and studies. For example, when evaluating imputation techniques aimed at prediction, different aims may be formulated than when statistical inference is of interest. The lack of consensus may also stem from different personal preference or scientific background. All in all, the lack of a common ground in evaluating imputation methodology may lead to sub-optimal use in practice. In this paper, we propose a move towards a standardized evaluation of imputation methodology. To demonstrate the need for standardization, we highlight a set of potential pitfalls that bring forth a chain of potential problems in the objective assessment of the performance of imputation routines.  Additionally, we suggest a course of action for simulating and evaluating missing data problems. Our suggested course of action is by no means meant to serve as a complete cookbook, but rather meant to incite critical thinking and a move to objective and fair evaluations of imputation methodology. We invite the readers of this paper to contribute to the suggested course of action.
\end{abstract}

@@

When evaluating the statistical properties - and thereby the practical applicability - of imputation methodology, researchers most often make use of simulation studies. Such studies are typically composed of an analysis pipeline in which data are subsequently generated, made incomplete, and imputed repeatedly under different simulation conditions. A set of evaluation criteria is then postulated to evaluate the performance of one or more missing data methods. Recent attention on best practices for method evaluation by means of simulation \citep{morr18} and \citet{pawe22}'s advice to pre-register simulation protocols will guide methodologist in conceptualizing their simulation workflow. However, there is no consensus on how to design, execute and report simulation studies aimed to evaluate imputation methodology. Without a `gold standard' for evaluation, the validity and comparability of simulation setups may differ tremendously from one developer to another. This brings forth a chain of potential problems in the objective assessment of imputation method performance within and across studies, which could lead to sub-optimal use of imputation in practice.

@@

Before setting up a simulation study, the simulator should clearly define and describe the scope of their evaluations. If the simulation parameters are unclear, any methodological problems with simulation study design may be obfuscated by the cognitive problem of generalization \citep{gree17}. For example, misinterpretation and (unintended) questionable research practices can prompt extrapolation beyond the scope of the simulations \citep{gree17, pawe22}. Imputation methods that seem to work well in simulations may then not be suitable in practice, when applied to incomplete empirical data.

One potential reason for discrepancies between imputation method performance in simulations versus applications is the use of sampling variance in the simulation design. Simulation studies on missing data methodology have the unique option to exclude sampling variance from their evaluations and only use the missing data generation procedure as the source of Monte Carlo variation \citep{vink14}. If sampling variance is not of interest, a single complete data set can serve as comparative truth in all simulation repetitions--as opposed to a `standard' simulation setup, in which data is drawn every repetition. After all, we are interested in solving for the missingness and have no need for the noise induced by the sampling mechanism for evaluation in such studies.

@@

A well-designed simulation does not guarantee fair evaluations. Estimands and other simulation targets should be clearly and unambiguously defined in the context of the study aim \citet{pete14}. The number of simulation repetitions may be informed by the required level of precision in the simulation study \citep[e.g. as determined from a maximum tolerable level of uncertainty in terms of a performance measure's Monte Carlo error; see][]{morr18}. The simulation design should ideally be fully factorial, i.e. varying each simulation condition against all other conditions. There may, for example, be interactions between the source and amount of missingness in the incomplete data and the efficacy of imputation methods--i.e., the validity of the assumed missingness mechanism becomes increasingly important with higher missingness proportions \citep{scho18}. If there is more than one imputation method under evaluation, the simulation design should apply each method to every incomplete data set. Applying all methods to the same incomplete data set is computationally convenient, and minimizes unnecessary variation, which makes for fairer comparisons.

@@

% [TODO: split up into data and missingness part of the DGM, with choices between data sources, missingness mechanisms and proportions. And divide problems between simulation and interpretation, see Reviewer 2: "whether method A (e.g. imputation) outperforms method B (e.g. listwise deletion) depends on the estimand, purpose of the study, used distributions (in the DGP, imputation model, possibly also analysis model), and simulation setup (e.g. dependency structure) - if a human misinterprets findings in a comparison of method A and B, then this is a cognitive problem and not the problem on how missingness was generated in the DGP."] 
%
%[TODO; describe problems with data generation and interpretation: If the source of the data is model-based, the correlations in the data may be so high that there is no effective missingness due to the predictive power in the other variables, and the data source may be unfair if the data generating model is equal to one of the imputation models under evaluation. With a design-based simulation, the data source is unlikely to have no missingness and the choice of initial missing data method may propagate into the evaluations.]

@@

\begin{figure}[t!]
  \resizebox{\textwidth}{!}{ %notice the \resizebox{} command
        \includegraphics{plots/plot_mmech.pdf}
  }      
  \caption{Three different realizations of missingness generation for MCAR and right-tailed MAR missingness mechanisms for different levels of correlation $\rho$ between the variable to ampute and the covariates that guide the probability to be missing. Note that the conditional probability of right-tailed MAR ($\rho=0$) mimics that of MCAR.}
    \label{Fig4}
\end{figure}

@@

The evaluation of simulated results goes far beyond plausibility and distributional characteristics. The quality and validity of an imputation task will also rely on the relation between the missing data models, imputation models, and analysis models. When a joint model exists whose conditionals would include the imputation and analysis model, then the imputation model and analysis are said to be congenial \citep{meng94, bart2015}. The congeniality of all imputation models should be assessed, but methods to assess the suitability of imputation models and diagnose misfit often rely on visual inspection of the imputations \citep[see e.g.][]{abayomi2008diagnostics, bond16}. This makes its assessment a challenging and timeconsuming endeavor in many simulation studies.

@@

\newpage

@@

\begin{table}[ht!]
\caption{Checklist for reporting on imputation methodology evaluations.}
\label{table:check}
\begin{tabular}{ll}
% \hline
%   & Suggested aspects to report                                                       \\
\hline
1 & Simulation scope                                                                   \\ \cline{2-2}
$\square$  & Aim                                                                                \\
$\square$  & Design (incl. pseudo-code or flow diagram)                                         \\
$\square$  & Number of simulation repetitions                                                   \\ \hline
2 & Comparative truth                                                                  \\ \cline{2-2}
$\square$  & Data source (model-based or design-based)                                           \\
$\square$  & Sampling variance                                                                  \\
%  & Data characteristics (number of observations, number of variables, variable types, \\
%  & coherence between variables incl. data structures e.g. clustering)                 \\
$\square$  & Data characteristics (incl. multivariate relations and structures e.g. clustering) \\
$\square$  & Estimand                                                                           \\ \hline 
3 & Induced missingness                                                                \\ \cline{2-2}
$\square$  & Missingness mechanism (incl. type or functional form of the missing data   model)  \\
$\square$  & Missingness pattern (incl. missingness proportion)                                 \\ \hline 
4 & Applied methods                                                                    \\ \cline{2-2}
$\square$  & Imputation methods (incl. parameters e.g. the number of imputations)               \\
$\square$  & Analytic methods (incl. calculation of standard errors e.g. pooling   rules)       \\
$\square$  & Reference method (e.g. complete case analysis)                                    \\ \hline 
5 & Imputation evaluation                                                              \\ \cline{2-2}
$\square$  & Imputation-generating process (e.g. algorithmic non-convergence)                   \\
$\square$  & Imputation model fit (e.g. posterior predictive checks)                            \\
$\square$  & Distributional characteristics (e.g. plausibility of imputed values)               \\ \hline 
6 & Performance evaluation                                                             \\ \cline{2-2}
$\square$  & Statistical properties (e.g. confidence validity)                                  \\
$\square$  & Comparative performance (e.g. predictive accuracy)                                 \\ \hline
\end{tabular}
\end{table}
